\documentclass[line]{res}
\usepackage{enumitem} % Allows for adding options to lists
\usepackage[left=1.25cm,right=2.5cm,vmargin=1.25cm]{geometry}

\author{Stuart Olivera}
\title{Stuart Olivera}

\begin{document}
\setlength{\textheight}{11.5in} % increase text height to fit on 1-page
\name{Stuart Olivera}
\address{\large
  42960 Deer Chase Pl
  \\
  Ashburn, VA 20147
  \\
  (703) 509-9523
}
\address{\it
  stuart@stuartolivera.com
  \\
  http://stuartolivera.com/
  \\
  http://linkedin.com/in/stuartolivera
}

\begin{resume}

\section{OBJECTIVE}

  A software development internship or co-op position for the Summer 2015 term, with special interest in web and mobile technologies.

\section{EDUCATION}

  Rochester Institute of Technology, Rochester, NY
  \hfill
  \textit{High School G.P.A. 3.65/4.0 (Current G.P.A TBD)}
  \\
  Bachelor of Science, Computer Science
  \hfill
  \textit{Expected Graduation Spring 2019}

\section{COMPUTER SKILLS}

  \begin{itemize}[leftmargin=10pt]
  \item Strong programming skills in Ruby, PHP, HTML, CSS, and JavaScript
  \item Working knowledge of Git, Ruby on Rails, AngularJS, SASS, and CoffeeScript
  \item Familiar with MySQL, MongoDB, and PostgreSQL databases
  \item Experience with test-driven development, project management, and open source contribution
  \end{itemize}

\section{EXPERIENCE}

  \textbf{Software Intern}
  \textit{BusyConf, LLC, Leesburg VA}
  \hfill
  Summer 2013 - Summer 2014\\
  Implemented sales-driving tactics for conference management solution in Ruby on Rails.
  Improved organizational tools in management interface.
  Enhanced front end interfaces and usability through jQuery UI and other open-source libraries.
  Migrated payment platfrom from BrainTree to Stripe.
  Responsible for integration with third party APIs.

  \textbf{Developer \& Designer, Owner}
  \textit{Olivera Web, LLC, Ashburn, VA}
  \hfill
  2009 - Present\\
  Provided custom designed websites for various businesses.
  Developed unique online software solutions to simplify and automate pre-existing tasks.
  Created and maintain hosting services for numerous websites of varying technologies.

\section{RELEVANT PROJECTS}

  \textbf{RIT Assassins}
  \hfill
  Summer 2014 - Present
  \\
  Front-end driven website to facilitate the game of Assassins at RIT, with future plans to support other hosts.
  Will provide tools for game organizers to initiate game, track progress, and evaluate "assassinations". Built in collaboration with other students using AngularJS alongside a REST-full API.

  \textbf{CSH 5K Registration}
  \hfill
  Fall 2014
  \\
  Website to promote and provide registration for a 5K fundraiser sponsored by Computer Science House at RIT.
  Responsible for integrating registration process and user interface.
  Integrated online billing through Stripe and in-person billing through Square.

  \textbf{DataMine}
  \hfill
  Spring 2013
  \\
  Online application for visualizing data sets and enabling public collaboration to data.
  Originated as a contestant to Microsoft's 2013 DreamSpark competition; no longer in development.

  \textbf{oWeb CMS}
  \hfill
  Spring 2011 - Summer 2013
  \\
  Custom content management system intended for simple and lightweight website management.
  Built in PHP and JavaScript/jQuery, featuring a basic plug-in system to allow for a common core among supported websites.

  \textbf{Open-Source Projects}
  \\
  Miscellaneous programs and contributions on http://github.com/sman591

\section{LEADERSHIP \& OTHER ACTIVITIES}
  \begin{itemize}[leftmargin=10pt]
  \item Active member of Computer Science House at the Rochester Institute of Technology
    \item Active recreational Skier \& Snowboarder
    \item Live sound engineer for bands, events, and shows
    \item Previously Technical Director for theatre department at Stone Bridge High School
  \end{itemize}

\end{resume}
\end{document}
